---
title: "The situation of COVID-19 in China and the corresponding analysis"
author: "Li Wenxuan"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Set the work path
```{r echo = TRUE}
# Please change the workpath into the file contains dataset
path <- 'C:/Users/(UserName)/Desktop/DataVisualization/Dataset_Visualization/'
```

## Import the packages we need
```{r echo = TRUE, warning = FALSE}
# Use tha packages: pacman to import the packages we need
# For packages that are not downloaded, pacman will download and load them
# For installed packages, pacman will load them directly
library(pacman)
library(barRacer)
pacman::p_load(choroplethr, corrplot, dplyr, DT, devtools,
               geosphere, gganimate, ggthemes, ggdark, ggplot2, 
               ggpubr, gifski, lubridate, magrittr, openair, paletteer, 
               plotly, RColorBrewer, readr, reshape2, rgdal,
               scales, tidyverse, tidyr, viridisLite, viridis)

# Avoid the language setting (Chinese) affect the plot
Sys.setlocale("LC_TIME", "English")
```

## Task 1: The overall situation of the COVID-19 outbreak in the world and China
1. Read the world map
```{r}
# read the world's map from choroplethrMaps
data(country.map, package = "choroplethrMaps")
#View(country.map)
```

2. Read the data of total death
```{r}
# read the data of world
World_data <- read.csv(paste0(path, "total_death_of_the_world.csv"),
                       stringsAsFactors = FALSE,
                       fileEncoding = "UTF-8")

# View(World_data)
```

3. Rename some countries or regions
```{r}
# rename some countries in the data to fit the map of the world
World_data <- World_data %>%
  mutate(sovereignt = recode(sovereignt,
                             "US" = "United States of America",
                             "Congo (Kinshasa)" = "Democratic Republic of the Congo",
                             "Congo (Brazzaville)" = "Republic of Congo",
                             "Korea, South" = "South Korea",
                             "Tanzania" = "United Republic of Tanzania",
                             "Serbia" = "Republic of Serbia",
                             "Burma" = "Myanmar"))

# set some limits and classes of data
World_data$Class <- cut(World_data$Deaths,
                        breaks = c(0, 100, 1000, 10000, 
                                   100000, 1000000, 10000000),
                        labels = c('[0 to 100]', '[100 to 1000]', 
                                   '[1000 to 10000]', '[10000 to 100000]',
                                   '[100000 to 1000000]', 
                                   '[1000000 to 10000000]'),
                        ordered_result = TRUE,
                        include.lowest = TRUE)

#View(World_data)
```

4. Draw the picture of total deaths in the world
```{r}
# merge the data and the map
World_data_temp <- merge(country.map, World_data, by = "sovereignt")

# sort the new map data to keep the picture in normal
World_data_temp <- World_data_temp[order(World_data_temp$id, 
                                         World_data_temp$order),]

#View(World_data_temp)

# draw the picture of the world
World <- ggplot() + 
  geom_polygon(data = World_data_temp,
               aes(x = long, y = lat, group = group, 
                   region = sovereignt, fill = Class, label = Deaths),
               color = "black") +
  #scale_fill_manual(values=c("green", "yellow", "orange", "red")) +
  scale_fill_brewer(palette="OrRd")

ggplotly(World)
```

5. Draw the picture of death in china
```{r}
# Read OGR vector maps into spatial objects
china_map <- readOGR(dsn = paste0(path, "CHN_adm"),
                     layer = "bou2_4p",
                     encoding = "GBK",
                     verbose = FALSE)

mydata <- china_map@data["NAME"]
mydata$id <- 0:924

mydata[mydata$id == 898, "NAME"] <- " "

mymapdata <- fortify(china_map)

mymapdata$id <- as.numeric(mymapdata$id)
mymapdata <- merge(mymapdata, mydata, all.x = TRUE)
mymapdata <- mymapdata %>% rename(region = NAME)

# read chinese data
China_data <- read.csv(paste0(path,"data_of_each_provinces_in_China.csv"),
                    fileEncoding = "GBK")

China_data$Death_Class <- cut(China_data$Deaths,
                       breaks = c(0, 10, 100, 1000, 10000),
                       labels = c('[0 to 10]', '[10 to 100]', '[100 to 1000]', '[1,000 to 10,000]'),
                       ordered_result = TRUE,
                       include.lowest = TRUE)

China_data$Confirmed_Class <- cut(China_data$Confirmed,
                       breaks = c(0, 100, 1000, 10000, 100000, 1000000),
                       labels = c('[0 to 100]', '[100 to 1000]', '[1000 to 10000]', '[10000 to 100000]',
                                  '[100000 to 1000000]'),
                       ordered_result = TRUE,
                       include.lowest = TRUE)

China_data_temp <- select(China_data, -c(jd, wd))
China_data_temp <- China_data_temp %>% rename(region = Province)

# merge the data and map and sort them
mymapdata_temp <- merge(mymapdata, China_data_temp, by = "region")
mymapdata_temp <- mymapdata_temp[order(mymapdata_temp$id, mymapdata_temp$order),]

#View(mymapdata_temp)

# draw the picture of china
China1 <- ggplot() + 
  geom_polygon(data = mymapdata_temp,
               aes(x = long, y = lat, group = group, region = region, fill = Confirmed_Class, 
                   label = Confirmed),
               color = "black") +
  #scale_fill_manual(values=c("green", "yellow", "orange", "red")) +
  scale_fill_brewer(palette="OrRd")

ggplotly(China1)
```

```{r}
China2 <- ggplot() + 
  geom_polygon(data = mymapdata_temp,
               aes(x = long, y = lat, group = group, region = region, fill = Death_Class, label = Deaths),
               color = "black") +
  #scale_fill_manual(values=c("green", "yellow", "orange", "red")) +
  scale_fill_brewer(palette="OrRd")

ggplotly(China2)
```

## Task 2: Showcase the situation of the COVID-19 outbreak in China
```{r}
ts_conf<-read.csv(paste0(path,"Cumulative_Confirmed_China.csv"),
                  fileEncoding = "UTF-8-BOM")
ts_death<-read.csv(paste0(path,"Cumulative_Death_China.csv"),
                   fileEncoding = "UTF-8-BOM")
names(ts_conf)
```

```{r}
#prepare for top data(confirm)
top_1<-t(ts_conf[831,-1])
top_1<-as.data.frame(top_1)
colnames(top_1)="conf"
top_1<-arrange(top_1,desc(conf))
province<-rownames(top_1)
top_1<-cbind(province,top_1)
```

```{r}
#prepare for top data(death)
top_2<-t(ts_death[831,-1])
top_2<-as.data.frame(top_2)
colnames(top_2)="death"
top_2<-arrange(top_2,desc(death))
province<-rownames(top_2)
top_2<-cbind(province,top_2)
```

```{r}
#plot of conf
top_1[1:6,] %>%
  ggplot(aes(x = reorder(`province`,conf), y = conf )) +
  geom_bar(stat = "identity", fill  = "deeppink", width = 0.8) +
  theme_economist() +
  scale_y_continuous(breaks = seq(0, 1500000, by = 150000), labels = comma) +
  coord_flip() +
  labs(x = "", y = "", title = "Top 6 (the Most Confirmed Cases)") +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(axis.title = element_text(size = 14, colour = "black"),
        axis.text.y = element_text(size = 11, face = "bold"))
```

```{r}
#plot of death
top_2[1:6,] %>%
  ggplot(aes(x = reorder(`province`,death), y = death )) +
  geom_bar(stat = "identity", fill  = "deepskyblue", width = 0.8) +
  theme_economist() +
  scale_y_continuous(breaks = seq(0, 10000, by = 1000), labels = comma) +
  coord_flip() +
  labs(x = "", y = "", title = "Top 6 (the Most Death Cases)") +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(axis.title = element_text(size = 14, colour = "black"),
        axis.text.y = element_text(size = 11, face = "bold"))
```

```{r}
#translate the format of data(add province)
ts_conf2<-gather(ts_conf,province,conf,Anhui,Beijing,Chongqing,Fujian,Gansu,Guangdong,
                 Guangxi,Guizhou,Hainan,Hebei,Heilongjiang,Henan,Hong_Kong,Hubei,
                 Hunan,Inner_Mongolia,Jiangsu,Jiangxi,Jilin,Liaoning,Macau,Ningxia,
                 Qinghai,Shaanxi,Shandong,Shanghai,Shanxi,Sichuan,Tianjin,Tibet,Taiwan,
                 Xinjiang,Yunnan,Zhejiang)
ts_death2<-gather(ts_death,province,death,Anhui,Beijing,Chongqing,Fujian,Gansu,Guangdong,
                 Guangxi,Guizhou,Hainan,Hebei,Heilongjiang,Henan,Hong_Kong,Hubei,
                 Hunan,Inner_Mongolia,Jiangsu,Jiangxi,Jilin,Liaoning,Macau,Ningxia,
                 Qinghai,Shaanxi,Shandong,Shanghai,Shanxi,Sichuan,Tianjin,Tibet,Taiwan,
                 Xinjiang,Yunnan,Zhejiang)
ts_comb<-cbind(ts_conf2,ts_death2$death)
ts_comb$Date <- as.Date(ts_comb$Date)
colnames(ts_comb)[1]<-"date"
colnames(ts_comb)[4]<-"death"
```

```{r}
#combine all data in 6 important city
data_top6 <- ts_comb %>%
  select('province', date, conf, death) %>%
  filter(`province` %in% c("Hong.Kong", "Hubei", "Shanghai", "Taiwan",
                                 "Jilin","Guangdong")) %>%
  group_by(`province`, date) %>%
  summarise(conf  = sum(conf),
            death = sum(death)) %>%
  mutate("New_Cases" = conf - lag(conf, 1),
         "Mortality_Rate" = death / conf) %>%
  mutate("New_Cases" = round(New_Cases, 3),
         "Mortality_Rate" = round(Mortality_Rate, 3))
data_top6$New_Cases[is.na(data_top6$New_Cases)] <- 0
data_top6$Mortality_Rate[is.nan(data_top6$Mortality_Rate)] <- 0
```

```{r}
data_top6 %>%
  ggplot(aes(x = date, y = Mortality_Rate, fill = province)) +
  geom_bar(stat = "identity",alpha = 0.8) +
  facet_wrap(~ province) +
  theme_minimal() +
  labs(x = "", y = "Mortality Rate") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",
        axis.title.y = element_text(face = "bold", size = 10))
```

```{r}
data_top6 %>%
  filter(date>"2022-04-01"&(province=="Jilin"|province=="Shanghai"))%>%
  ggplot(aes(x = date, y = New_Cases, fill = province)) +
  geom_bar(stat = "identity",alpha = 0.8) +
  facet_wrap(~ province) +
  theme_minimal() +
  labs(x = "", y = "New Cases") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",
        axis.title.y = element_text(face = "bold", size = 10))
```


```{r}
data_top6 %>%
  filter(date >="2022-04-01") %>%
  select('province', date, conf) %>%
  rename(Names = province) %>%
  gather(Status, Cases, -c("date", "Names")) %>%
  ggplot(aes(x = date, y = Cases, fill = as.factor(Names) ) ) +
  geom_bar(stat = "identity", color = "black")+
  scale_fill_brewer(palette = "Pastel1") +
  facet_grid(.~Status) +
  labs(x = "", y= "", fill = "") +
  theme_economist_white() +
  theme(legend.position = "bottom", legend.direction = "horizontal",
        legend.text =element_text(face = "bold", size = 8))
```

```{r}
#prepare for data of shanghai and jilin
new1<-cbind(ts_conf$Date,ts_conf$Shanghai,ts_conf$Jilin,ts_death$Shanghai,ts_death$Jilin)
colnames(new1)<-c("date","conf_S","conf_J","death_S","death_J")
new1<-as.data.frame(new1)
new1$date <- as.Date(new1$date)
new1<-na.omit(new1)
```

```{r}
new1$conf_S<-as.numeric(new1$conf_S)
new1$conf_J<-as.numeric(new1$conf_J)
new1$death_S<-as.numeric(new1$death_S)
new1$death_J<-as.numeric(new1$death_J)
#shanghai
new1 <- new1 %>%
  group_by(date, conf_S) %>%
  mutate(Mortality_rate_S = (death_S)/(conf_S)) %>%
  ungroup()
#jilin
new1 <- new1 %>%
  group_by(date, conf_J) %>%
  mutate(Mortality_rate_J = (death_J)/(conf_J)) %>%
  ungroup()
#change nan into 0
new1[is.na(new1)]<-0
```

```{r}
barchart_1 <-new1 %>%
  select(date,Mortality_rate_S,Mortality_rate_J) %>%
  gather(status.ratio, ratio, -date ) %>%
  ggplot(aes(x = date, y = ratio, fill = status.ratio)) +
  geom_bar(stat = "identity", position = "dodge") +
    theme(plot.margin = margin(0, 0, 0, 0, "pt"),
          panel.background = element_rect(fill = "White"),
          legend.position = "bottom",
          axis.title = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank()) +
    ggtitle("The Mortality_rate")

ggplotly(barchart_1) %>%
layout(legend = list(orientation = 'h'))
```


## Task 3: Comparison of the epidemic situation in Shanghai City and Jilin Province in 2022  
### View the changes in the cumulative number of confirmed/Deaths cases in main places in 2022
```{r}
# 1. Cumulative confirmed cases
cumulative_confirmed <- read.csv(paste0(path,'Cumulative_Confirmed_China.csv'))
cumulative_confirmed$Date <- as.Date(cumulative_confirmed$Date)
cumulative_confirmed <- melt(cumulative_confirmed,
                             id = 'Date')
cumulative_confirmed <- cumulative_confirmed %>%
  filter(variable == 'Jilin' |
         variable == 'Shanghai' |
         variable == 'Hong_Kong' |
         variable == 'Taiwan') %>%
  filter(Date >= as.Date('2022-01-01') & 
         Date < as.Date('2022-05-01'))
cumulative_confirmed$Date <- ymd(cumulative_confirmed$Date)

barracer_confirmed <- bar_chart_race(cumulative_confirmed, variable, value, Date, 
                                     title ="Changes in the Cumulative Confirmed Cases in 2022")

# Save the Gif
gganimate::anim_save('Changes in Cumulative Confirmed Cases in 2022.gif')

barracer_confirmed
```

```{r}
# 2. Cumulative deaths cases
cumulative_deaths <- read.csv(paste0(path,'Cumulative_Death_China.csv'))
cumulative_deaths$Date <- as.Date(cumulative_deaths$Date)
cumulative_deaths <- melt(cumulative_deaths,
                          id = 'Date')
cumulative_deaths <- cumulative_deaths %>%
  filter(variable == 'Jilin' |
         variable == 'Shanghai' |
         variable == 'Hong_Kong' |
         variable == 'Taiwan') %>%
  filter(Date >= as.Date('2022-01-01') & 
         Date < as.Date('2022-05-01'))
cumulative_deaths$Date <- ymd(cumulative_deaths$Date)

barracer_deaths <- bar_chart_race(cumulative_deaths, variable, value, Date, 
                                  title ="Changes in the Cumulative Death Cases in 2022")

# Save the Gif
gganimate::anim_save('Changes in Cumulative Death Cases in 2022.gif')

barracer_deaths
```

### Comparison of cumulative confirmed cases and cumulative deaths between the two places
```{r echo = TRUE}
# Import the data we need in this task
cumulative_data <- read.csv(paste0(path,"Cumulative_data_each_provinceOrState.csv"),
                            encoding = "UTF-8")

# Generate the cumulative data of Shanghai City and Jilin Province
cumulative <- cumulative_data %>%
  filter(Province_State == 'Jilin' |
         Province_State == 'Shanghai')
print(cumulative)

# Pie Chart of Cumulative Confirmed Data
cumulative_confirmed <- cumulative %>%
  mutate(prop = round(Confirmed * 100 / sum(Confirmed), 1),
         lab.ypos = cumsum(prop) - 0.5*prop)
cumulative_confirmed$label <- paste0(cumulative_confirmed$Province_State, '\n',
                                     'Cases: ',
                                     cumulative_confirmed$Confirmed,'\n',
                                     'Ratio: ',
                                     round(cumulative_confirmed$prop,2), '%')

pie_confirmed <- ggplot(cumulative_confirmed, 
                        aes(x = ' ', y = prop,
                            fill = Province_State))+
  geom_col(fill = c('#FAA43AFF','#5DA5DAFF'),
           direction = -1) +
  geom_text(aes(y = lab.ypos, label = label),
            size = 3,
            color = "black") +
  coord_polar(theta = "y")+
  scale_color_paletteer_d("basetheme::minimal")+
  theme_void() +
  theme(legend.position = "FALSE")

# Pie Chart of Cumulative Deaths Data
cumulative_deaths <- cumulative %>%
  mutate(prop = Deaths * 100 / sum(Deaths),
         lab.ypos = cumsum(prop) - 0.5 * prop )
cumulative_deaths$label <- paste0(cumulative_deaths$Province_State, '\n',
                                  'Cases: ',
                                  cumulative_deaths$Deaths,'\n',
                                  'Ratio: ',
                                  round(cumulative_deaths$prop,2), '%')
pie_deaths <- ggplot(cumulative_deaths,
                     aes(x = ' ', y = prop,
                         fill = Province_State))+
  geom_col(fill = c('#FAA43AFF','#5DA5DAFF'),
           direction = -1) +
  geom_text(aes(y = lab.ypos, label = label),
            size = 3,
            color = "black") +
  coord_polar(theta = "y")+
  theme_void() +
  theme(legend.position = "FALSE")

# Bar Chart of Cumulative Confirmed Data
cumulative_melt <- melt(cumulative, 
                             id = c('Province_State','Country_Region'))

cumulative_melt_comfirmed<- cumulative_melt %>%
  filter(variable == 'Confirmed')

barplot_confirmed <- ggplot(cumulative_melt_comfirmed,
                            aes(x = Province_State, 
                                y = value))+
  geom_col(position = 'dodge',
           fill = c('#FAA43AFF','#5DA5DAFF'),
           width = 0.5)+
  geom_text(aes(label = value),
            size = 3,
            color = 'black',
            vjust = -0.25) +
  scale_y_continuous(limits = c(0, 80000))+
  labs(x = 'Province / City',
       y = 'Cases',
       title = "Cumulative Confirmed Cases",
       subtitle = 'Shanghai City vs. Jilin Province')+
  theme_bw()

# Bar Chart of Cumulative Deaths Data
cumulative_melt_deaths<- cumulative_melt %>%
  filter(variable == 'Deaths')

barplot_deaths <- ggplot(cumulative_melt_deaths,
                         aes(x = Province_State, 
                             y = value))+
  geom_col(position = 'dodge',
           fill = c('#FAA43AFF','#5DA5DAFF'),
           width = 0.5)+
  geom_text(aes(label = value),
            size = 3,
            color = 'black',
            vjust = -0.25) +
  scale_y_continuous(limits = c(0, 600))+
  labs(x = 'Province / City',
       y = 'Cases',
       title = "Cumulative Deaths Cases",
       subtitle = 'Shanghai City vs. Jilin Province')+
  theme_bw()

# Use ggarrange to combine these plots
plot2 <- ggarrange(barplot_confirmed,pie_confirmed, 
                   barplot_deaths, pie_deaths,
                   ncol = 2, nrow = 2,
                   widths = 1,
                   heights = 3)

# Show the result of plot1
plot2
```

### Comparison of daily confirmed cases and daily deaths between the two places in 2022
```{r echo = TRUE}
# Plot2: The distribution of 4 time series
# 1. Cumulative confirmed cases
cumulative_confirmed <- read.csv(paste0(path,'Cumulative_Confirmed_China.csv'))
cumulative_confirmed$Date <- as.Date(cumulative_confirmed$Date)
cumulative_confirmed <- melt(cumulative_confirmed,
                             id = 'Date')
cumulative_confirmed <- cumulative_confirmed %>%
  filter(variable == 'Jilin' |
         variable == 'Shanghai') %>%
  filter(Date >= as.Date('2022-01-01') & 
         Date < as.Date('2022-05-01'))

ts_cumulative_confirmed <- ggplot(cumulative_confirmed,
                                  aes(x = Date,
                                      y = value,
                                      color = variable,
                                      group = variable))+
  geom_line(size = 1,linetype = 2) +
  scale_x_date(date_labels="%d", 
               date_breaks="week",
               expand=c(0,0))+
  scale_y_continuous(limits = c(0,60000),
                     expand  = c(0,0))+
  facet_grid(~month(Date,label=T),
             space="free_x",                
             scales="free_x",           
             switch="y") + 
  scale_fill_brewer(palette = "Set1")+
  labs(x = ' ',
       y = 'Cases',
       title = "Cumulative Confirmed Cases in 2022",
       subtitle = 'Shanghai City vs. Jilin Province')+
  theme_bw()+
  theme(legend.title=element_blank())

# 2. Daily Confirmed Cases
daily_confirmed <- read.csv(paste0(path,'Daily_Confirmed_China.csv'))
daily_confirmed$Date <- as.Date(daily_confirmed$Date)
daily_confirmed <- melt(daily_confirmed,
                        id = 'Date')
daily_confirmed <- daily_confirmed %>%
  filter(variable == 'Jilin' |
         variable == 'Shanghai') %>%
  filter(Date >= as.Date('2022-01-01') & 
         Date < as.Date('2022-05-01'))

ts_daily_confirmed <- ggplot(daily_confirmed,
                             aes(x = Date,
                                 y = value,
                                 color = variable,
                                 group = variable))+
  geom_line(size = 1,linetype = 1) +
  geom_ribbon(aes(ymin = 0, ymax =  value, 
                  group = variable,fill = variable),
              alpha = 0.5)+

  scale_x_date(date_labels="%d", 
               date_breaks="week",
               expand=c(0,0))+
  scale_y_continuous(limits = c(0,6000),
                     expand  = c(0,0))+
  facet_grid(~month(Date,label=T),
             space="free_x",                
             scales="free_x",           
             switch="y") + 
  scale_fill_brewer(palette = "Set1")+
  labs(x = ' ',
       y = 'Cases',
       title = "Daily Confirmed Cases in 2022",
       subtitle = 'Shanghai City vs. Jilin Province')+
  theme_bw()+
  theme(legend.title=element_blank())

# 3. Cumulative Death Cases
cumulative_death <- read.csv(paste0(path,'Cumulative_Death_China.csv'))
cumulative_death$Date <- as.Date(cumulative_death$Date)
cumulative_death <- melt(cumulative_death,
                        id = 'Date')
cumulative_death <- cumulative_death %>%
  filter(variable == 'Jilin' |
         variable == 'Shanghai') %>%
  filter(Date >= as.Date('2022-01-01') & 
         Date < as.Date('2022-05-01'))

ts_cumulative_death <- ggplot(cumulative_death,
                              aes(x = Date,
                                  y = value,
                                  color = variable,
                                  group = variable))+
  geom_line(size = 1,linetype = 2) +
  scale_x_date(date_labels="%d", 
               date_breaks="week",
               expand=c(0,0))+
  scale_y_continuous(limits = c(0,400),
                     expand  = c(0,0))+
  facet_grid(~month(Date,label=T),
             space="free_x",                
             scales="free_x",           
             switch="y") + 
  scale_fill_brewer(palette = "Set1")+
  labs(x = ' ',
       y = 'Cases',
       title = "Cumulative Death Cases in 2022",
       subtitle = 'Shanghai City vs. Jilin Province')+
  theme_bw()+
  theme(legend.title=element_blank())

# 4. Daily Death Cases
daily_death <- read.csv(paste0(path,'Daily_Death_China.csv'))
daily_death$Date <- as.Date(daily_death$Date)
daily_death <- melt(daily_death,
                    id = 'Date')
daily_death <- daily_death %>%
  filter(variable == 'Jilin' |
         variable == 'Shanghai') %>%
  filter(Date >= as.Date('2022-01-01') & 
         Date < as.Date('2022-05-01'))

ts_daily_death <- ggplot(daily_death,
                         aes(x = Date,
                             y = value,
                             color = variable,
                             group = variable))+
  geom_line(size = 1,linetype = 1) +
  geom_ribbon(aes(ymin = 0, ymax =  value, 
                  group = variable,fill = variable),
              alpha = 0.5)+

  scale_x_date(date_labels="%d", 
               date_breaks="week",
               expand=c(0,0))+
  scale_y_continuous(limits = c(0,60),
                     expand  = c(0,0))+
  facet_grid(~month(Date,label=T),
             space="free_x",                
             scales="free_x",           
             switch="y") + 
  scale_fill_brewer(palette = "Set1")+
  labs(x = ' ',
       y = 'Cases',
       title = "Daily Death Cases in 2022",
       subtitle = 'Shanghai City vs. Jilin Province')+
  theme_bw()+
  theme(legend.title=element_blank())

# Use ggarrange to combine there plot
plot2 <- ggarrange(ts_cumulative_confirmed,ts_daily_confirmed, 
                   ts_cumulative_death, ts_daily_death,
                   ncol = 2, nrow = 2,
                   widths = 3,
                   heights = 1.5,
                   common.legend = T,
                   legend = 'bottom')

plot2
```